tecks
========

```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE
)
```

[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Build Status](https://travis-ci.com/sckott/tecks.svg?branch=master)](https://travis-ci.com/sckott/tecks)

Wrapper for Python's [bibtexparser](https://bibtexparser.readthedocs.io) [src](https://github.com/sciunto-org/python-bibtexparser)

the `bibtex` pkg may or may not be getting attention moving forward - maybe this will help in the meantime ...

**BEWARE: VERY ALPHA**

## Installation

```{r eval=FALSE}
remotes::install_github("sckott/tecks")
```

```{r}
library("tecks")
```

## read bibtex file

```{r}
z <- system.file("extdata/bib-many.bib", package = "tecks")
out <- teck_read(path = z)
out
names(out)
```

`entries` is probably the thing you want

```{r}
out$entries
```

## Meta

* Please [report any issues or bugs](https://github.com/sckott/tecks/issues).
* License: MIT
* Get citation information for `tecks` in R doing `citation(package = 'tecks')`
* Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.
